---
title: "Predicting if price reduction will lead to an increase in sales"
author: "ELegushi Adetunji"
date: "3/20/2022"
output: 
        github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This lab will be used to show if factors like price deduction,coupon usage and cart will lead to increase in sales.

Use this data to determine how these factors influence sales.

Predict sales of canned tomatoes during a week in which you use a shopping cart notice, a coupon, and reduce price by 1 cent.



```{r library}
#loading the library 
library(pacman)
p_load(tidyverse,statsr,broom,openintro,janitor,infer,readxl)
library(broom)


```


```{r summary}
#loading the data
Grocery <- read_excel("C:/Users/adeju/Downloads/Grocery.xlsx")
glimpse(Grocery)

```

```{r cleaning the data}

Grocery %>% 
  clean_names()->Grocery

```


Performing EDA

```{r looking for relationship}
library(GGally)
ggpairs(Grocery)

```

```{r modelling}
#using the linear model 
m =lm(sales ~ coupon+cart_notice+ price_reduction, data = Grocery)


```



```{r}
summary(m)
```

### Interpreting the model

intercept= this means that when all the predictors used (coupon,cart_notice,price_reduction) are all zero then we can expect to  sell 14.5 cases of tomatoes per. This is usually not the case for this store bcause at one point in time a customer might use their coupon.

`coupon` = this has two levels, when the coupon was used and when it was not used, analysing the report here means, when the coupon was yes or used() at -1.167, sales went down by -1.167 than when it was not used and looking at the p_value, this is not a good predictor of sales and in the new model, it will be removed.

`cart_notice` = another categorical data, yes or no, this indicates that, when cart was used the model predicts that sales will increase by 20.167. A good predictor
of sales.

`price_reduction` = this is a numerical variable, and according to the model, when there is price reduction, the model predicts that sales will go up by 6.375

Looking at the the R-Squared, its is high but removing coupon will increase the r-squared in an improved model.

To forecast using the model, the linear equation will be
sales = 14.5-1.167(coupon)+20.167(cart_notice)+6.375(price_reduction)


A new model will be used and compared to the previous r-squared to see the winner, in this model, coupon will be removed.

```{r moddel 2}
m2 =lm(sales ~cart_notice+ price_reduction, data = Grocery)

```

looking at the coefficients
```{r}
summary(m2)

```

looking at the model, the adjusted r-squared as increased from 0.84 to 0.85 and the second model did a better job at predicting sales.
we can either use forecast manually or use the predict fuction.

```{r prediction1}
p=data.frame(cart_notice ="Yes", price_reduction = 2)

```

```{r prediction}
predict(m2,p,interval = "prediction",level = 0.95)

```
the model predict with a confidence level  of 0.95 that when price reduction is at 2% and cart_notice is yes, sales might increase and will always  be between 
$34 and $58.

looking at sales for that period 

```{r sales}
Grocery %>% 
  filter(cart_notice == "Yes" & price_reduction == 2) %>% 
select(cart_notice,price_reduction,sales)
```


The model predicted that sales will always between $34 and $58 and looking at when sales is 40 a nd 44 in the original dataand  when price reduction is 2 and cart_notice is yes, sales is between $40 and $44.


##Observations
We can conclude that when there is price reduction  all things being held equal,sales might increase.
We can also say that when cart_notice is yes sales might increase too as long as every other variable is held equal.




